These classes provide optional additional functions to \mbox{\hyperlink{classPHPMailer}{P\+H\+P\+Mailer}}.

These are not loaded by the \mbox{\hyperlink{classPHPMailer}{P\+H\+P\+Mailer}} autoloader, so in some cases you may need to {\ttfamily require} them yourself before using them.

This class was originally written by Manuel Reinhard and provides a simple means of generating I\+C\+S/v\+Cal files that are used in sending calendar events. \mbox{\hyperlink{classPHPMailer}{P\+H\+P\+Mailer}} does not use it directly, but you can use it to generate content appropriate for placing in the {\ttfamily Ical} property of \mbox{\hyperlink{classPHPMailer}{P\+H\+P\+Mailer}}. The \mbox{\hyperlink{classPHPMailer}{P\+H\+P\+Mailer}} project is now its official home as Manuel has given permission for that and is no longer maintaining it himself.

This class by Konstantin Riabitsev and Jim Jagielski implements H\+T\+ML filtering to remove potentially malicious tags, such as {\ttfamily $<$script$>$} or {\ttfamily onclick=} attributes that can result in X\+SS attacks. This is a simple filter and is not as comprehensive as \href{http://www.bioinformatics.org/phplabware/internal_utilities/htmLawed/}{\texttt{ H\+T\+M\+Lawed}} or \href{http://htmlpurifier.org}{\texttt{ H\+T\+M\+L\+Purifier}}, but it\textquotesingle{}s easier to use and considerably better than nothing! \mbox{\hyperlink{classPHPMailer}{P\+H\+P\+Mailer}} does not use it directly, but you may want to apply it to user-\/supplied H\+T\+ML before using it as a message body.

This class by Manuel Lemos (bundled with permission) adds the ability to authenticate with Microsoft Windows mail servers that use N\+T\+L\+M-\/based authentication. It is used by \mbox{\hyperlink{classPHPMailer}{P\+H\+P\+Mailer}} if you send via \mbox{\hyperlink{classSMTP}{S\+M\+TP}} and set the {\ttfamily Auth\+Type} property to {\ttfamily N\+T\+LM}; you will also need to use the {\ttfamily Realm} and {\ttfamily Workstation} properties. The original source is \href{http://www.phpclasses.org/browse/file/7495.html}{\texttt{ here}}. 